Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
motivation links in

>>>>

Motivation in specific social machines has been studied, including motivation of participants
in: Wikipedia~\cite{kuznetsov2006motivations}; Open Source Software~\cite{lakhani2003hackers};
Peer-to-peer filesharing~\cite{p2p}; Tagging~\cite{tagging}; and Virtual
Communities~\cite{ardichvili2003motivation,Moore:2007:UMM:1235000.1235035}.

[relate this work back to ours briefly.]
